The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-01-25 src/ms.tex
Add citations

Likewise, JWST developers have provided significant contributions to
the \package{photutils}, \package{specutils}, and \package{regions}
coordinated packages and the \package{gwcs} affiliated package. For
example, development of the \package{photutils} coordinated package
for source detection and photometry has largely been led by JWST
contributions. JWST developers have also made significant contributions
to the \package{specutils} coordinated package, which is used for
analyzing spectroscopic data, and the \package{regions} coordinated
package, which is used to handle geometric regions. The \package{gwcs}
affiliated package for generalized world coordinate systems was created
specifically to handle the complex world coordinate systems needed
for JWST spectroscopic data. Further, the \package{ASDF} (Advanced
Scientific Data Format) package, a next-generation interchange format
for scientific data, was initially developed at STScI to serialize JWST
WCS objects along with \astropypkg models, units, and coordinates. Over
its mission lifetime, JWST will continue its support in developing and
maintaining these critically dependent packages.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }

>>>>

Likewise, JWST developers have provided significant contributions
to the \package{photutils} \citep{photutils}, \package{specutils}
\citep{specutils}, and \package{regions} \citep{regions} coordinated
packages and the \package{gwcs} \citep{gwcs} affiliated package. For
example, development of the \package{photutils} coordinated package
for source detection and photometry has largely been led by JWST
contributions. JWST developers have also made significant contributions
to the \package{specutils} coordinated package, which is used for
analyzing spectroscopic data, and the \package{regions} coordinated
package, which is used to handle geometric regions. The \package{gwcs}
affiliated package for generalized world coordinate systems was created
specifically to handle the complex world coordinate systems needed
for JWST spectroscopic data. Further, the \package{ASDF} (Advanced
Scientific Data Format) package \citep{ASDF}, a next-generation
interchange format for scientific data, was initially developed at STScI
to serialize JWST WCS objects along with \astropypkg models, units, and
coordinates. Over its mission lifetime, JWST will continue its support
in developing and maintaining these critically dependent packages.

@@

\software{\package{astropy} \citep{astropy:2013, astropy:2018},
          \package{numpy} \citep{numpy:nature},
          \package{scipy} \citep{scipy},
          \package{matplotlib} \citep{matplotlib},
          \package{Cython} \citep{cython},
          \package{photutils} \citep{photutils},
          \package{specutils} \citep{specutils},
          \package{regions} \citep{regions},
          \package{gwcs} \citep{gwcs},
          \package{ASDF} \citep{ASDF}.
        %   \package{SOFA} \citep{sofa},
        %   \package{ERFA} (\citealt{erfa})
          }
